% !TeX root = main.tex
%------------------------
% Resume Template
% Author : Sina Shabani Kumeleh
% Github : https://github.com/itzloop
% License : MIT
%------------------------
\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[a4paper]{article}
\usepackage{commands}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\setlength{\tabcolsep}{0in}

\definecolor{CompanyDescColor}{HTML}{808080}

\begin{document}
\begin{center}
  \textls[160]{\huge\bfseries \MakeUppercase{Sina Shabani Kumeleh}}
\end{center}
\vspace*{1pt}
\begin{center}
  \textls[80]{\Large\bfseries \MakeUppercase{Senior Software Engineer}}
\end{center}
\rule{\textwidth}{1pt}
\vspace{40pt}
\begin{minipage}[t]{0.3\textwidth}
  \preparetopsec
  \section{contacts}
  {
    \href{tel:+989395536558}{\faIcon{mobile-alt} \small~~(+98) 939-553-6558} \\ \vspace{6pt}  
    \href{mailto:sina.sh.k78@gmail.com}{\faIcon{envelope} \small~~sina.sh.k78@gmail.com} \\ \vspace{6pt} 
    \href{https://github.com/itzloop}{\faIcon{github-square} \small~~github.com/itzloop}\\ \vspace{6pt} 
    \href{https://linkedin.com/in/sina-shabaniku}{\faIcon{linkedin} \small~~linkedin.com/sina-shabaniku} \\ \vspace{6pt} 
    \faIcon{map-marker-alt} \small~~Tehran, Iran
    \vspace*{14pt}
  }

  \preparenormalsec
  \section{skills}
  {
    \skill
      {Software Engineering}
      {Testing and Test Automation, Continuous Integration and Continuous Delivery (CI/CD), System Design, Distributed Systems, Scalability, Networking}
    \vspace*{6pt}
    \skill
      {Languages and Tools}
      {Golang, Bash, Python, Java, C/C++, C\#, JS, TS, Node, Lua, Kubernetes, Docker, Apache Kafka, Redis, PostgreSQL, Ansible, Git, Nginx, Linux, WebRTC, Helm}
  }
  \preparenormalsec
  \section{education}
  {
    \edu
      {Bachelor of Software Engineering}
      {https://www.linkedin.com/school/iran-university-of-science-and-technology/}
      {Iran University of Science and Technology}
      {}
  }
  \preparenormalsec
  \section{volunteering}
  {

     \volunteer
     {\href{https://www.linkedin.com/posts/cesa-iust_قراره-با-هم-دنیای-وب-رو-زیر-و-رو-کنیم-activity-7221917118215180288-SRca/?rcm=ACoAACBgw1ABKvTqrlXwvAbFBul6vPHXEMeIFWw}{Bootcamp Lead Instructor}}
      {\href{https://www.linkedin.com/company/cesa-iust/}{CESA IUST}}
      {CESA is the student's scientific association of the department of computer engineering, Iran University of Science and Technology.}
    
      \vspace*{6pt}

     \volunteer
      {\href{https://www.linkedin.com/posts/sina-shabaniku_techroad-activity-7201269217688436736-C0G2?utm_source=share&utm_medium=member_desktop&rcm=ACoAACBgw1ABKvTqrlXwvAbFBul6vPHXEMeIFWw}{Conference Speaker}}
      {\href{https://www.linkedin.com/company/cesa-iust/}{CESA IUST}}
      {}

    \vspace*{6pt}

    \volunteer
      {Teaching Assistant}
      {Operating Systems Course at \href{https://www.linkedin.com/school/iran-university-of-science-and-technology/}{IUST}}
      {}

    \vspace*{6pt}

    \volunteer
      {Backend Bootcamp Instructor}
      {\href{https://www.linkedin.com/company/cesa-iust/}{CESA IUST}}
      {}

    \vspace*{6pt}

    \volunteer
      {Git Workshop Instructor}
      {\href{https://www.linkedin.com/company/cesa-iust/}{CESA IUST}}
      {}
  }
\end{minipage}
\hspace{20pt}
\begin{minipage}[t]{0.65\textwidth}
  \preparetopsec
  \section{perofessional summary}
    \begin{justify}
      \begin{footnotesize}
Results-driven Senior Software Engineer with 5+ years of experience in backend 
development, technical leadership, and cloud-native architectures. Currently working
as a Backend Chapter Lead, defining technical strategies and best practices 
to optimize backend architecture and developer experience. Previously led a cross-functional 
team of 7, building real-time WebRTC systems with 500K+ daily calls.
      \end{footnotesize}
    \end{justify}
  \preparenormalsec
  \section{work experience}
  {
    \expheadingwithlink
      {Backend Chapter Lead}
      {Bale Messanger}
      {https://www.linkedin.com/company/balemessenger/}
      {Mar 2021 - Present}
      {Bale is a Fast and handy Payment and Communication platform built upon a safe messaging and financial system with over 4 million daily active users.}
    \begin{itemize}[leftmargin=.5cm, itemsep=1pt]
        \item 
            \begin{small}
                \textbf{\emph{Backend Chapter Lead}} \newline
                \begin{justifying}\small 
                    Leading backend technical strategy and improving architecture and development workflows
                \end{justifying}
            \end{small}
        \item
            \begin{small}
                \textbf{\emph{Team Lead}} \newline
                \begin{justifying}\small 
                    Managed a cross-functional team of 7 to build a real-time WebRTC system, supporting 500K+ daily calls with a 68\% CSat.
                \end{justifying}
            \end{small}
        \item
            \begin{small}
                \textbf{\emph{Senior Software Engineer}} \newline
                \begin{justifying}\small 
                    Developed and managed a real-time video/audio platform, handling 2 million daily calls and 51K+ hours of communication with an 80\% satisfaction rate.
                \end{justifying}
            \end{small}
        \item
            \begin{small}
                \textbf{\emph{Software Engineer}} \newline

            \begin{itemize}[leftmargin=.5cm, itemsep=1pt]
                \item
                    \begin{justifying}\small 
                        Created a money-sharing service for special occasions, processing 10,000+ packets daily and facilitating transactions exceeding 2 billion rials.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Built a USSD-based one-way communication service for the annual Arbaeen walk.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Enhanced deployment and test automation by introducing CI/CD tools and building robust test suites.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Led the infrastructure design for Saﬁr, a B2B product, promoting Bale's messaging as an alternative to SMS.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Developed a wrapper for the IRDR (Central Bank of Iran's cryptocurrency), improving the National Bank of Iran’s wallet functionality.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Created an advertisement monetization service that became the primary revenue source for 3 years.
                    \end{justifying}
                \item
                    \begin{justifying}\small 
                        Built a wrapper for the National Bank of Iran’s wallet to enable micro-transactions like ECharge and Internet payments.
                    \end{justifying}
            \end{itemize}
            \end{small}
  \end{itemize}

  \expheadingwithlink
    {Game Developer}
    {Medrick FZE}
    {https://www.linkedin.com/company/medrick-fze/}
    {Nov 2019 - Jul 2020}
    {Medrick is a video game publisher and development company founded in 2008 with the intention of developing and publishing AAA mobile and PC games in the MENA region.}

    \begin{itemize}[leftmargin=.5cm]
      \item \justifying\small Created a game client for Dicer, a digital adaptation of Yahtzee, originally introduced by Milton Bradley and later acquired by Hasbro in 1956.
    \end{itemize}
  }
\end{minipage}

\vspace{-1pt}
\rule{\textwidth}{1pt}
\end{document}
